\section{Introduction}\label{Sec:introduction} 
This report is based mainly on a couple of papers, which are correlated: the first one is \cite{caravaggio_nonlinear_2018}, in which I have chosen the a continuous time model and in particular the model briefly described in the subsection 4.1 called \textit{"The Antoci-Russu-Galeotti Model"}, and the second one is \cite{antoci_poverty_2011}, the one containing the full description. Nonetheless other third part papers could be involved and cited. 

As Antoci \cite{antoci_poverty_2011} pointed out in the paper, equilibrium selection in dynamic optimization models with externalities may depend on expectations; that is, given the initial values of the state variables (history), the path followed by the economy maybe determined by the choice of the initial values of the jumping variables. This implies that expectations play a key role in equilibrium selection and in fact global indeterminacy may occur: that is, starting from the same initial values of the state variables, different equilibrium paths can approach different $\omega$-limit sets (for example, different attractive stationary states). In this context, local stability analysis may be misleading, in that it refers to a neighborhood of a stationary state, whereas the initial values of jumping variables do not have to belong to such a neighborhood. In words of Matsuyama \cite{matsuyama_increasing_1991} p. 619:
\textit{“Knowing the local dynamics is not enough, because, for example, demonstrating the uniqueness of the perfect foresight path in a neighborhood of a stationary state does not necessarily rule out the existence of other perfect foresight paths in the large.”}

Although some works on indeterminacy focus on global dynamics and stress the relevance of global analysis, the literature on indeterminacy is almost exclusively based on local analysis, due to the fact that dynamic models exhibiting indeterminacy are often highly nonlinear and difficult to be analyzed globally. Few papers study global indeterminacy in environmental dynamics, see references in \cite{antoci_poverty_2011}. \\
In the present work the authors were not dealing with another important problem in economic dynamics, namely the existence of indifference points in an optimal control problem. Starting from these points, several optimal solutions exist, giving rise to the same value of the objective function. Vice versa, in our context, as it happens to be the case in the literature on indeterminacy, the trajectories followed by the economy are Nash equilibria but do not represent optimal solutions, being the dynamics conditioned by externalities. Therefore, when multiple Nash equilibrium trajectories exist, starting from the same initial values of the state variables, economic agents may select one which is Pareto-dominated by others, due to coordination problems.

The objective of the paper \cite{antoci_poverty_2011} is to highlight the relevance of global indeterminacy in a context in which economic activity depends on the exploitation of a free-access natural resource. They analyzed a growth model with environmental externalities, giving rise to a three-dimensional nonlinear dynamic system (the framework is that introduced by Wirl in \cite{wirl_stability_1997}). In particular they studied the equilibrium growth dynamics of an economy constituted by a continuum of identical agents. At each instant of time $t$, the representative agent produces the output $Y(t)$ by labor $L(t)$, by the accumulated physical capital $K(t)$ and by the stock $E(t)$ of an open-access renewable natural resource. The economy-wide aggregate production $Y(t)$ negatively affects the stock of the natural resource; however, the value of $Y(t)$ is considered as exogenously determined by the representative agent, so that economic dynamics is affected by negative environmental externalities.\footnote{Environmental externalities can affect economic activities especially in developing countries, where property rights tend to be ill-defined and ill-protected, environmental institutions and regulations are weak and natural resources are more fragile than in developed countries, which are located in temperate areas instead than in tropical and sub-tropical regions.}

They assumed that the representative agent’s instantaneous utility, depending on leisure $1-L(t)$ and consumption $C(t)$ of the output $Y(t)$, is represented by the additively non-separable function $\frac{[C(1-L)^{\epsilon}]^{1-\eta} -1}{1-\eta}$. Moreover, we assume that the production technology is represented by the Cobb–Douglas function $[K(t)]^\alpha [L(t)]^\beta [E(t)]^\gamma$, with $\alpha + \beta < 1$ and $\alpha$, $\beta$, $\gamma \,>0$. 

In this context, we show that, if $\alpha + \beta < 1$, the dynamics can admit a locally attracting stationary state (also equilibria or fixed point) $P_1^* = (K_1^*, E_1^*, L^*)$, in fact a \textit{poverty trap}, coexisting with another stationary state $P_2^* = (K_2^*,E_2^*,L^*)$, where $K_1^* < K_2^*$ and $E_1^* < E_2^*$, possessing saddle-point stability.\\ 
Global analysis shows that, under some conditions on the parameters, if the economy starts
from initial values $K_0$ and $E_0$ sufficiently close to $K_1^*$ and $E_1^*$, then there exists a continuum of initial values $L_0^1$ such that the trajectory from $(K_0,E_0,L_0^1)$ approaches $P_1^*$ and a locally unique initial value $L_0^2$ such that the trajectory from $(K_0,E_0,L_0^2)$ approaches $P_2^*$ (see Figure \ref{fig:local_indeter}). Therefore, their model exhibits local indeterminacy (i.e. there exists a continuum of trajectories leading to $P_1^*$), but also global indeterminacy, since either $P_1^*$ or $P_2^*$ may be selected according to agents’ expectations. Along the trajectories belonging to the basin of attraction of $P_1^*$, over-exploitation
of the natural resource drives the economy towards a \textit{tragedy of commons} scenario (later explained).

These results are obtained through a partial description of the shape of the saddle-point two dimensional stable manifold. A full description of such a manifold is usually very difficult or impossible. However, in a three-dimensional system, two-dimensional stable (or unstable) manifolds are separatrices between different regimes of the trajectories. Therefore, if one is able to detect, in a significant region of the phase space, a separatrix between two sets of points whose trajectories show different behavior, that may lead to relevant information on the manifold of interest. Also it must be stressed that gaining information on separatrices is paramount to any global analysis: in particular it can lead to information on size and/or shape of attractive basins (which several authors in different works cited in \cite{antoci_poverty_2011} consider the main goal of global indeterminacy analysis).\\ 
For example Wirl \cite{wirl_sustainable_2004} analyzes a separatrix problem in an optimal growth model where, differently from this case, the only production factor is physical capital $K$ and a renewable environmental resource $R$ enters only into the utility function. The analytical context is also quite different from the underlying work. In fact Wirl considers optimal solutions for a four dimensional system exhibiting two saddle-point stable stationary states. It turns out that in the two-dimensional state space $(K,R)$ the basins of attraction of the two stable stationary states are separated by a curve, whose corresponding optimal trajectories lie on the one-dimensional stable manifold of a third conditionally stable stationary point. Moreover, Wirl shows the possible existence of limit cycles around the stationary states, arisen through Hopf bifurcations. Vice versa, in this work they analyzed a three-dimensional system whose trajectories are sub-optimal Nash solutions of a dynamical control problem. In such a context the two-dimensional stable manifold of a saddle-point stable stationary state may separate, in the three-dimensional phase space, the basin of attraction of another Pareto-dominated stationary state (a poverty trap) from a region whose trajectories tend to a boundary point where the economy collapses (i.e. physical capital and labor tend to zero, while the environmental resource tends to its carrying capacity). The possible existence of limit cycles, generated by Hopf bifurcations, is shown also in this work, through numerical simulations implemented by me.

The paper \cite{antoci_poverty_2011} also contains some results from numerical simulations, which provide further insights about the dynamics of the model (which I will newly perform):
\begin{itemize}
	\item Global indeterminacy may occur also in the context which $P_1^*$ has a stable manifold of dimension one and $P_2^*$ is either saddle-point stable or repelling (three positive real part eigenvalues), and thus no locally indeterminate stationary state exists. In such a context, numerical simulations show that, in case $P_2^*$ is a saddle-point, then, starting from the same initial values of $K$ and $E$, the economy may approach either the determinate stationary state $P_2^*$ or an attracting limit cycle surrounding $P_1^*$ (see Figure \ref{fig:limit_cyc_P1_from_P2}). Vice versa, when $P_2^*$ is a source (i.e. repelling), simulations indicate the possible existence of two limit cycles (see Figure \ref{fig:limit_cyc_P1_P2}), so that, starting from the same initial values of $K$ and $E$, the economy may approach either
	an attracting limit cycle surrounding $P_1^*$ or a limit cycle endowed with a two-dimensional stable manifold surrounding $P_2^*$.
	\item Numerical simulations suggest that the stable manifold of the locally determinate point $P_2^*$ bounds the basin of attraction of the locally indeterminate point $P_1^*$ or of the attracting cycle around $P_1^*$ (see Figs. \ref{fig:local_indeter}, \ref{fig:limit_cyc_P1_from_P2}). This implies that even if the economy starts very close to the locally determinate point $P_2^*$, it can move quite far away from it, in particular toward a poverty trap.
\end{itemize}

This analysis focuses on global indeterminacy of dynamics, but it also gives sufficient conditions for local indeterminacy. There exists an enormous literature on local indeterminacy in economic growth models. Although in the article \cite{antoci_poverty_2011} they did not have room for a review, they pointed out the place that their results occupy in the current research. In fact, even if the main body of the literature on local indeterminacy concerns economies with increasing social returns, a growing proportion of articles deals with models where indeterminacy is obtained under the assumption of social constant return technologies. In this paper \cite{antoci_poverty_2011}, local indeterminacy can occur with social constant or decreasing returns and is generated by negative environmental externalities of production activity affecting the natural resource. Other works focus on the role played by negative externalities in producing local  indeterminacy. For examples see the paper \cite{antoci_poverty_2011} p. 573.

The present work has the following structure. Section \ref{Sec:model_dyn} defines the set-up of the model and the associated dynamic system. Section \ref{Sec:fix_pnt_stab_Hopf_bif} deals with the existence and local stability of stationary states and with Hopf bifurcations arising from stability changes. Section \ref{Sec:glob_anal_conclusion} is devoted to the global analysis of dynamics and provides the main results of the paper. 

